\textbf{ \Large {Reducing data traffic in wireless structural health monitoring systems using embedded computing}}

### 2015-02-10 Paper/PaperJahrSchlichSHM.tex
minor finfishing touches

The structure is excited by deflecting and releasing the top of the structure.
This excitation method ensures a free vibration in natural frequency with little interferences.
After excitation, when the acceleration threshold is exceeded, the sensor nodes automatically start measuring the acceleration.
To minimize the wireless data traffic, each sensor node performs a FFT, once sufficient acceleration measurements have been collected.
By the use of the FFT, the acceleration measurements are converted into the oscillation frequencies and the corresponding magnitudes of the building.

@@

\begin{figure}[htb]
    \centering
    \includegraphics[scale=0.9]{figures/50Hz.pdf}
    \caption{frequency domain graph of the oscillation}
    \label{fig:50hzfft}
\end{figure}

>>>>

The structure is excited by deflecting and releasing the top of the structure.
This excitation method ensures a free vibration in natural frequency with little interferences.
After excitation, when the acceleration threshold is exceeded, the sensor nodes automatically start measuring the acceleration.
To minimize the wireless data traffic, each sensor node performs a FFT, once sufficient acceleration measurements have been collected.
By the use of the FFT, the acceleration measurements are converted into the oscillation frequencies and the corresponding magnitudes of the building \cite{rao2011fast}.

@@

\begin{figure}[htb]
    \centering
    \includegraphics[scale=0.9]{figures/76HzHalf.pdf}
    \caption{frequency domain graph of the oscillation}
    \label{fig:76hzfft}
\end{figure}
